---
title: "Error Logging in R"
output:
  pdf_document: default
  html_notebook: default
---

## Using Purr

- Found some useful tools to test functions in R.
- Came across some good links as well linked to this.
- This ['{R-bloggers}'](https://www.r-bloggers.com/2022/03/capture-errors-warnings-and-messages/) link has some good information on this.
- I think I am also liking the chronicler package by ['{Bruno Rodrigues}'](https://www.brodrigues.co/).

```{r}
#Let's use my package normfluodbf
library(normfluodbf)
fpath <- system.file("extdata", "dat_2.dat", package = "normfluodbf", mustWork = TRUE)

#Using safely
safe_log = purrr::safely(normfluodat)
a = safe_log(dat=fpath, tnp = 3, cycles = 40)

#Using quietly
quiet_log = purrr::quietly(normfluodat)
b = quiet_log(dat=fpath, tnp = 3, cycles = 40)

# Based on the results I clearly see that quietly captures the message while safely fails to capture the message.
```
## Using TryCatch

- Check out the function I cooked up based on some information from ['{Datatechnotes}'](https://www.datatechnotes.com/2017/09/logging-into-file-in-r-scripts.html). That is a good way to log error files locally and have them in hand for debugging. 

## Using Chronicler
- Seems to have some benchmarking abilities as well. Did not dive deep into it but like the way it works so far.

```{r}
# Some snippets from Bruno's chronicler found on github
# I am rewriting because that page is found on my iPad

rsqrt = chronicler::record(sqrt)
a = rsqrt(1:5)
a

#get just the values
chronicler::pick(a,'value')
chronicler::pick(a,'log_df')

#get the log and this gives run time
chronicler::read_log(a)
```
